Probability Distribution Checks

### 2017-04-25 Analysis.Rmd
Revise analysis and data handling
**_THIS IS BEING REVISED_**

The original analysis is unlikely to be the correct approach. The data
are being examined again and a new analysis will be conducted that
accounts for the ordinal scale used for data collection for severity.

The data are now in a tidy data frame and are ready for checking
Calculate AUDPS for tiller sheath blight incidence
Double check tiller sheath blight incidence calculations, there is a
negative AUDPS value in 2015 data

@@

## 2015
### 2015 Leaf Sheath Blight Severity Model
```{r 2015_LShB}

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
LShB_lmm_2015 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE,
                          random = ~REP, 
                          data = as.data.frame(AUDPS_2015),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

summary(LShB_lmm_2015)

# create data frames for generating diagnostic plots
reps <- data.frame(LShB_lmm_2015$Sol[, c(1, 7:10)])
x <- 1:nrow(reps)
reps <- melt(reps)

trts <-  data.frame(LShB_lmm_2015$Sol[, 2:6])
trts <- melt(trts)

# Create a dummy x-axis variable for plotting
x <- 1:nrow(LShB_lmm_2015$Sol)

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2015 Diagnostic Plots for Replicates, Leaf ShB Severity")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2015 Reps Replicate Posteriors for Replicates, Leaf ShB Severity")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2015 Diagnostic Plots for Treatments, Leaf ShB Severity")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2015 Posteriors for Treatments, Leaf ShB Severity")

# check random effects
plotTrace(LShB_lmm_2015$VCV, log = TRUE)

# plot joint distibution of error
rdf <- data.frame(LShB_lmm_2015$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2015 Random Error Distribution for Leaf ShB Severity"))
```

### 2015 Tiller Sheath Blight Severity Model
```{r 2015_TShB}

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_severity_lmm_2015 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE,
                                   random = ~REP, 
                          data = as.data.frame(AUDPS_2015),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

summary(TShB_severity_lmm_2015)

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_severity_lmm_2015$Sol[, c(1, 7:10)])
reps <- melt(reps)

trts <-  data.frame(TShB_severity_lmm_2015$Sol[, 2:6])
trts <- melt(trts)

# Create a dummy x-axis variable for plotting
x <- 1:nrow(TShB_severity_lmm_2015$Sol)

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2015 Diagnostic Plots for Replicates, Tiller ShB Severity")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2015 Reps Replicate Posteriors for Replicates, Tiller ShB Severity")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2015 Diagnostic Plots for Treatments, Tiller ShB Severity")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2015 Posteriors for Treatments, Tiller ShB Severity")

# check random effects
plotTrace(TShB_severity_lmm_2015$VCV, log = TRUE)

# plot joint distibution of error
rdf <- data.frame(TShB_severity_lmm_2015$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2015 Random Error Distribution for Tiller ShB Severity"))
```

@@

### 2016 Leaf Sheath Blight Severity Model
```{r 2016_LShB}

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
LShB_lmm_2016 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE,
                          random = ~REP, 
                          data = as.data.frame(AUDPS_2016),
                          verbose = FALSE,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          prior = eprior,
                          pr = TRUE)

summary(LShB_lmm_2016)

# create data frames for generating diagnostic plots
reps <- data.frame(LShB_lmm_2016$Sol[, c(1, 5:8)])
reps <- melt(reps)

trts <-  data.frame(LShB_lmm_2016$Sol[, 2:4])
trts <- melt(trts)

# Create a dummy x-axis variable for plotting
x <- 1:nrow(LShB_lmm_2016$Sol)

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2016 Diagnostic Plots for Replicates, Leaf ShB Severity")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2016 Reps Replicate Posteriors for Replicates, Leaf ShB Severity")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2016 Diagnostic Plots for Treatments, Leaf ShB Severity")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2016 Posteriors for Treatments, Leaf ShB Severity")

# check random effects
plotTrace(LShB_lmm_2016$VCV, log = TRUE)

# plot joint distibution of error
rdf <- data.frame(LShB_lmm_2016$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2016 Random Error Distribution for Leaf ShB Severity"))
```

### 2016 Tiller Sheath Blight Severity Model
```{r 2016_TShB}

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_severity_lmm_2016 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE,
                                   random = ~REP, 
                          data = as.data.frame(AUDPS_2016),
                          verbose = FALSE,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          prior = eprior,
                          pr = TRUE)

summary(TShB_severity_lmm_2016)

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_severity_lmm_2016$Sol[, c(1, 5:8)])
reps <- melt(reps)

trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:4])
trts <- melt(trts)

# Create a dummy x-axis variable for plotting
x <- 1:nrow(TShB_severity_lmm_2016$Sol)
# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2016 Diagnostic Plots for Replicates, Tiller ShB Severity")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2016 Reps Replicate Posteriors for Replicates, Tiller ShB Severity")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2016 Diagnostic Plots for Treatments, Tiller ShB Severity")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2016 Posteriors for Treatments, Tiller ShB Severity")

# check random effects
plotTrace(TShB_severity_lmm_2016$VCV, log = TRUE)

# plot joint distibution of error
rdf <- data.frame(TShB_severity_lmm_2016$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2016 Random Error Distribution for Tiller ShB Severity"))
```

>>>>

**_THIS IS BEING REVISED_**

This analysis is unlikely to be the correct approach. The data are being examined
again and a new analysis will be conducted that accounts for the ordinal scale
used for data collection for severity.

However, these analyses should be correct for the tiller sheath blight incidence.

@@

## 2015

@@

### 2017-04-25 Probability_distribution_checks.Rmd
Calculate AUDPS for tiller sheath blight incidence
Double check tiller sheath blight incidence calculations, there is a
negative AUDPS value in 2015 data

```{r, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(DS2015$TShB_incidence, "norm")
plot(f1)
car::qqp(DS2015$TShB_incidence, "norm")

f2 <- fitdist(DS2015$TShB_incidence, "exp")
plot(f2)
car::qqp(DS2015$TShB_incidence, "exp")

@@

```{r, results='hide', message=FALSE, warning=FALSE}

f1 <- fitdist(DS2016$TShB_incidence, "norm")
plot(f1)
car::qqp(DS2016$TShB_incidence, "norm")

f2 <- fitdist(DS2016$TShB_incidence, "exp")
plot(f2)
car::qqp(DS2016$TShB_incidence, "exp")

>>>>

```{r, results='hide', message=FALSE, warning=FALSE}
AUDPS15 <- subset(AUDPS, YEAR == "2015")
f1 <- fitdist(AUDPS15$TShB_incidence, "norm")
plot(f1)
car::qqp(AUDPS15$TShB_incidence, "norm")

f2 <- fitdist(AUDPS15$TShB_incidence, "exp")
plot(f2)
car::qqp(AUDPS15$TShB_incidence, "exp")

@@

```{r, results='hide', message=FALSE, warning=FALSE}
AUDPS156 <- subset(AUDPS, YEAR == "2016")
f1 <- fitdist(AUDPS156$TShB_incidence, "norm")
plot(f1)
car::qqp(AUDPS156$TShB_incidence, "norm")

f2 <- fitdist(AUDPS156$TShB_incidence, "exp")
plot(f2)
car::qqp(AUDPS156$TShB_incidence, "exp")
